Graph Generators for Data Science: A Survey

### 2018-06-05 introduction.tex
A few paragraphs in the introduction

In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application. Gartner Inc.\footnote{\url{http://www.gartner.com/}} describes Big Data as ``\emph{high \textbf{v}olume, high \textbf{v}elocity, and/or high \textbf{v}ariety information assets that require new forms of processing to enable enhanced decision making, insight discovery and process optimization}''.

\TODO{there are two types of graph big data sets - large graphs and large sets of small graphs; we focus on the former one}

\paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:
\begin{itemize}
  \item ...
\end{itemize}

@@

To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and 
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IOT, Telecommunication and graph streaming generators, 
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

>>>>

%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application. Gartner Inc.\footnote{\url{http://www.gartner.com/}} describes Big Data as ``\emph{high \textbf{v}olume, high \textbf{v}elocity, and/or high \textbf{v}ariety information assets that require new forms of processing to enable enhanced decision making, insight discovery and process optimization}''.

%\TODO{The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.}

One of the most popular data structures in the world of computer science are graphs. They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background. With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular. There has appeared a number of use cases\footnote{\url{https://neo4j.com/use-cases/}} (such as fraud detection, recommendation engines, social networks etc.) where graphs represent the linked information.

In general, we can distinguish two types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}. Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}. In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern. Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for manipulation with the data is proposed). As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

In this survey we ... \TODO{We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities}

... \TODO{Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.}

... \TODO{We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.}

... \TODO{This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.}

\paragraph*{Contributions} The key contributions of this survey are as follows:
\begin{itemize}
  \item ...
\end{itemize}

@@

To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

### 2018-06-05 main.tex
A few paragraphs in the introduction

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Data Generators in the World of Big Data}

@@

\begin{abstract}
%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
%...
The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data. We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Data Generators in the World of Big Data.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

>>>>

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators for Data Science: A Survey}

@@

\begin{abstract}
The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data. We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Generators for Data Science: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
